Federated Imputation

### 2020-06-21 federated_imp_synthesizing_complete_data.Rmd
Update r markdown

@. Impute the `boys` dataset with `m=1`, which results in the completed `boyscomp` data.
@. Over `i` in `1:nsim(=1000)` iterations, the output following output is collected:
  + The regression estimates of `nsim` times synthesized complete dataset.
  + The regression estimates of `nsim` times the synthesized partitioned dataset.
  + The regression estimates of `nsim` times the synthesized `nsim` times partitioned dataset.
@. Over `nsim` iterations, the average estimates are calculated ($\bar{Q}$), the bias ($\mu_Q - \bar{Q}$), the confidence intervals averaged over all iterations, and the coverage ($\frac{1}{nsim} \sum_{i = 1}^{nsim} Lower_i < \mu_Q < Upper_i$).

@@

```{r}
knitr::kable(syn_out)
```

>>>>

@. Impute the `boys` dataset with `m=1`, which results in the completed `boyscomp` data.
@. Over `i` in `1:nsim(=1000)` iterations, the output following output is collected:
  + The regression estimates of `nsim` times synthesized complete dataset.
  + The regression estimates of `nsim` times the synthesized partitioned dataset.
  + The regression estimates of `nsim` times the synthesized `nsim` times partitioned dataset.
@. Over `nsim` iterations, the average estimates are calculated ($\bar{Q}$), the bias ($\mu_Q - \bar{Q}$), the confidence intervals averaged over all iterations, and the coverage ($\frac{1}{nsim} \sum_{i = 1}^{nsim} LLCI_i < \mu_Q < ULCI_i$).

@@

```{r, echo = F}
knitr::kable(syn_out, digits = 3, caption = "Simulation results of the model age ~ hgt + tv for three different synthesizing")
```

# References

\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\noindent

<div id="refs"></div>
